### 2019-10-24 manuscript/manuscript.rmd
fix published analyses axis labels

analyses_published %>%
	ggplot( aes(x=model_summary, y=clade, col=result, shape=inference) ) +
		geom_jitter( width = 0.20, height = 0.20, alpha=0.7, size=2 ) +
		scale_colour_manual(values = result_colors) +
		theme_classic()

>>>>

analyses_published %>%
	ggplot( aes(x=model_combined, y=clade, col=result, shape=inference) ) +
		geom_jitter( width = 0.20, height = 0.20, alpha=0.7, size=2 ) +
		scale_colour_manual(values = result_colors) +
		theme_classic() + theme(axis.text.x = element_text(angle=45, hjust=1))
